---
title: "README for `tmdbdata` R Package"
output:
  github_document:
  # html_notebook:
    toc: true
    toc_depth: 3
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Installation

<!-- badges: start -->

<!-- badges: end -->

The goal of `tmdbdata` is to serve as an API wrapper and access data from [The Movie Database's (TMDB) Application Programming Interface (API)](https://developer.themoviedb.org/docs/getting-started)

You can install the development version of tmdbdata from [GitHub](https://github.com/) with:


```{r load tmdb, warning=F, message=F}
# install.packages("devtools")
# devtools::install_github("novakowd/tmdbdata")
# library(tmdbdata)

devtools::load_all() # Development version of library(tmdbdata)
```


```{r load other packages, warning=F, message=F}
# Other packages used in this file
library(tidyverse)
library(httr2)
```

## Authentication {#authentication}

This package must be supplied with an **API Read Access Token** for the functions to interact with the API.\

Otherwise the API server will throw an error message:

```{r error=T}
search_movies(query = "Avengers",
              auth_token = "invalid") # Example Only, never hardcode secrets (see below)
```

To obtain an Access Token, follow the steps in the [***API's documentation***](https://developer.themoviedb.org/docs/authentication-application).\
Once you have the access token, **DO NOT** hardcode it into a script

``` r
# ❗ NEVER DO THIS
auth_token <- "YOUR_AUTH_TOKEN"
```

❗ **DANGER**: Hardcoding secrets/passwords can pose [significant security risks](https://docs.github.com/en/get-started/learning-to-code/storing-your-secrets-safely)

Instead, it is better to store the Access Token as a *`environment variable`*, which is retrieved automatically via the [function defaults](https://httr2.r-lib.org/articles/wrapping-apis.html#user-supplied-key) **`auth_token = get_auth_token()`**

Here are **2** options that can help set the `TMBD_AUTH_TOKEN` environment variable:

### Option 1: `.Renviron` (RECOMMENDED)

This is the preferred method because the token will be available in future R sessions.

``` r
usethis::edit_r_environ() 
# type `TMDB_AUTH_TOKEN=YOUR_AUTH_TOKEN` in the `.Renviron` that opened,
# then save the file
```

### Option 2: `set_auth_token()` (Temporary Solution)

This needs to be run every time R is opened/restarted, so **Option 1** is preferred.

``` r
set_auth_token() 
# type `YOUR_AUTH_TOKEN` in dialogue, Need to re-run every session
```

***

# Examples

##### Search For Movies
```{r}
avenger_movies <- search_movies(query = "Avengers", 
                                num_pages = 1) 

avenger_movies %>% glimpse()
```

##### Get Movie Details
```{r}
avenger_movie_details <- movie_details(
  movie_id = avenger_movies$id[1],
  append_to_response = "videos,images,keywords"
)

avenger_movie_details$belongs_to_collection
avenger_movie_details$runtime %>% paste("minutes")
avenger_movie_details$genres
```

***

# TMDB data functions with `httr2::functions()`

This Package uses [**`httr2` package**](https://httr2.r-lib.org/articles/wrapping-apis.html) functions to generate and perform requests then extract results from the response body.

## Create Basic Request

A **`base_tmdb_request`** is constructed by looking at settings found in the [**API documentation**](https://developer.themoviedb.org/docs/rate-limiting).

For example:

-   **`req_headers()`** info in the [**Response Format**](https://developer.themoviedb.org/docs/json-and-jsonp) and [**Authentication**](https://developer.themoviedb.org/docs/authentication-application) Documentation.\
-   **`req_throttle()`** info in the [**Rate Limits Documentation**](https://developer.themoviedb.org/docs/rate-limiting)

```{r}
base_tmdb_request
```

> | 📝 | default of `auth_token = get_auth_token()`, will **only** work with option 1 or 2 (environment variable) as mentioned [**above**](#authentication) |
> |-----------------------------|:------------------------------------------|

The `Authorization` header info is also redacted in the following objects.

------------------------------------------------------------------------

Running the above `base_tmdb_request()` function generates a basic `<httr2_request>` object:

```{r, echo=F}
base_tmdb_request()
```

> The functions `req_headers()`, `req_error()`, `req_user_agent()`, and `req_throttle()` do NOT change the URL `https://api.themoviedb.org/3/`, but they DO add other elements to the request such as `Headers`, `Options`, and `Policies`.

------------------------------------------------------------------------

## Append Request Details

The next step is to append a path to the base URL and add relevant arguments to help with the request. Find appropriate arguments by consulting the API Documentation.

The below example looks at the [**Search\>Movie Documentation**](https://developer.themoviedb.org/reference/search-movie) which states:

-   there is a **required** parameter called **`query`** and,
-   some other *optional* parameters, some of which have default values.

Let's try putting together a request to **`search`** the **`movies`** for **`Avengers`**:

```{r}
base_tmdb_request() %>% 
  req_url_path_append("search","movie") %>% 
  req_url_query(query = "Avengers")
```

> The functions `req_url_path_append()` and `req_url_query()` modified the url to **`r base_tmdb_request() %>% req_url_path_append("search", "movie") %>% req_url_query(query = "Avengers") %>% pluck("url")`**

------------------------------------------------------------------------

## Perform Request

Now that we have built a request, **`req_perform()`** allows us to get a `response`.

-   **`req_perform()`** submits the request to the server 
    -     assigning to a `variable` stores the response in-memory, as to not exceed the API's [Rate Limits](https://developer.themoviedb.org/docs/rate-limiting)

```{r}
response <- base_tmdb_request() %>% 
  req_url_path_append("search", "movie") %>% 
  req_url_query(query = "Avengers") %>% 
  req_perform()

response
```

### Response Structure

Printing the `<httr2_response>` object above does not show much information, though more information is available when inspecting closer:

```{r}
class(response)
```

```{r}
data.frame(class = unlist(lapply(response,class)),
           length = unlist(lapply(response,length)))
```

```{r}
names(response$headers)
```

The actual 'Data' that we're looking for is in the `$body` element, though it appears to be in a raw hexadecimal format:

```{r}
cat(response$body[1:30], "...")
```

## Response Body

[**`httr2`**](https://httr2.r-lib.org/) provides many [`resp_body_*()`](https://httr2.r-lib.org/reference/resp_body_raw.html) functions to extract the `body` data, depending on the API response format(s).\
The [**API Documentation**](https://developer.themoviedb.org/docs/json-and-jsonp) states the **only supported response format is `JSON`**, so we use the **`resp_body_json()`** function and use the `simplifyVector = T` to make the resulting lists easier to work with.

```{r}
body <- response %>% 
  resp_body_json(simplifyVector = T)
```

Inspecting the body shows it is a list with 4 elements.  

```{r}
lapply(body, class)
```

The `$page`, `$total_pages`, and `$total_results` elements are all `integer` values:

```{r}
body[c("page", "total_pages", "total_results")]
```

The `$results` element is a `data.frame`

```{r}
body$results %>% 
  glimpse()
```

### Missing Data

The `body$total_results` is `r body$total_results`, yet the `body$results` only contain `r nrow(body$results)` rows.\
This is because **`r paste("body$total_pages =", body$total_pages)`** but each response only returns **one** page.

To get the other pages, we need to specify an additional argument **`page = n`** to the response, like so:

```{r}
page2_response <- base_tmdb_request() %>% 
  req_url_path_append("search", "movie") %>% 
  req_url_query(query = "Avengers",
                page = 2) %>%                ### NEW ARGUMENT
  req_perform() %>% 
  resp_body_json(simplifyVector = T) 

page2_response %>% 
  pluck('results') %>% 
  glimpse()
```

This 'second page' table contains the *next* `r nrow(page2_response$results)` rows.\
To get all rows we need to repeat this until `r paste("page =", page2_response$total_pages)`
