---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tmdbdata

<!-- badges: start -->
<!-- badges: end -->

The goal of `tmdbdata` is to serve as an API wrapper and access data from [The Movie Database's (TMDB) Application Programming Interface (API)](https://developer.themoviedb.org/docs/getting-started)

## Installation

You can install the development version of tmdbdata from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("novakowd/tmdbdata")
```
```{r include=F}
devtools::load_all()
```


## Authentication {#authentication}

This package must be supplied with an **API Read Access Token** for the functions to interact with the API.\

Otherwise the API server will throw an error message:

```{r echo=F}
invalid_auth_token <- "INVALID_AUTH_TOKEN"
```


```{r error=T}
search_movies(query = "Avengers",
              auth_token = invalid_auth_token)
```

To obtain an Access Token, follow the steps in the [***API's documentation***](https://developer.themoviedb.org/docs/authentication-application).\
Once you have `YOUR_AUTH_TOKEN`, store it in a [environment variable](https://httr2.r-lib.org/articles/wrapping-apis.html#user-supplied-key)

+   storing in the `.Renviron` file means the variable will be available in future R sessions

``` r
usethis::edit_r_environ() 
# type `TMDB_AUTH_TOKEN=YOUR_AUTH_TOKEN` in the `.Renviron` that opened,
# then save the file
```

> `set_auth_token()` will also set the `TMDB_AUTH_TOKEN` environment variable, but it is only specific to the session you're working in  

The package's functions can now be used as the default argument `auth_token = get_auth_token()` will automatically get this environment variable

***

# Examples

##### Search For Movies
```{r}
avenger_movies <- search_movies(query = "Avengers", 
                                num_pages = 1) 

avenger_movies %>% dplyr::glimpse()
```

##### Get Movie Details
```{r}
avenger_movie_details <- movie_details(
  movie_id = avenger_movies$id[1],
  append_to_response = "keywords"
)

avenger_movie_details %>% dplyr::glimpse()
```
