---
title: "tmdbdata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tmdbdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=F}
library(tmdbdata)
library(dplyr)
library(tidyr)
library(httr2)
```


# TMDB data functions with `httr2::functions()`

This Package uses [**`httr2` package**](https://httr2.r-lib.org/articles/wrapping-apis.html) functions to generate and perform requests then extract results from the response body.

## Create Basic Request

A **`base_tmdb_request`** is constructed by looking at settings found in the [**API documentation**](https://developer.themoviedb.org/docs/rate-limiting).

For example:

-   **`httr2::req_headers()`** info in the [**Response Format**](https://developer.themoviedb.org/docs/json-and-jsonp) and [**Authentication**](https://developer.themoviedb.org/docs/authentication-application) Documentation.\
-   **`httr2::req_throttle()`** info in the [**Rate Limits Documentation**](https://developer.themoviedb.org/docs/rate-limiting)

```{r}
base_tmdb_request
```

> | ðŸ“ | default of `auth_token = get_auth_token()`, will **only** work after the environment variable has been setup as mentioned in [**Authentication**](https://novakowd.github.io/tmdbdata/#authentication) |
> |-|:----------------------------------------------------|

The `Authorization` header info is also redacted in the following objects.

------------------------------------------------------------------------

Running the above `base_tmdb_request()` function generates a basic `<httr2_request>` object:

- Normally `auth_token` should not need to be specified if the [Authentication](https://novakowd.github.io/tmdbdata/#authentication) steps were followed

```{r eval = secret_has_key("HTTR2_KEY")}
base_request <- base_tmdb_request(auth_token = decrypt_auth_token())
base_request
```

The functions `req_headers()`, `req_error()`, `req_user_agent()`, and `req_throttle()` do NOT change the URL `https://api.themoviedb.org/3/`, but they DO add other elements to the request such as `Headers`, `Options`, and `Policies`.

------------------------------------------------------------------------

## Append Request Details

The next step is to append a path to the base URL and add relevant arguments to help with the request. Find appropriate arguments by consulting the API Documentation.

The below example looks at the [**Search\>Movie Documentation**](https://developer.themoviedb.org/reference/search-movie) which states:

-   there is a **required** parameter called **`query`** and,
-   some other *optional* parameters, some of which have default values.

Let's try putting together a request to **`search`** the **`movies`** for **`Avengers`**:

```{r}
base_request %>% 
  req_url_path_append("search","movie") %>% 
  req_url_query(query = "Avengers")
```

> The functions `req_url_path_append()` and `req_url_query()` modified the url to `r base_request %>% req_url_path_append("search", "movie") %>% req_url_query(query = "Avengers") %>% purrr::pluck("url")`

------------------------------------------------------------------------

## Perform Request

Now that we have built a request, **`httr2::req_perform()`** allows us to get a `response`.

-   **`httr2::req_perform()`** submits the request to the server 
    -     assigning to a `variable` stores the response in-memory, as to not exceed the API's [Rate Limits](https://developer.themoviedb.org/docs/rate-limiting)

```{r}
response <- base_request %>% 
  req_url_path_append("search", "movie") %>% 
  req_url_query(query = "Avengers") %>% 
  req_perform()

response
```

### Response Structure

Printing the `<httr2_response>` object above does not show much information, though more information is available when inspecting closer:

```{r}
class(response)
```

```{r}
data.frame(class = unlist(lapply(response,class)),
           length = unlist(lapply(response,length)))
```

```{r}
names(response$headers)
```

The actual 'Data' that we're looking for is in the `$body` element, though it is not in a usable format yet:

```{r}
response$body %>% glimpse()
```

## Response Body

[**`httr2`**](https://httr2.r-lib.org/) provides many [`resp_body_*()`](https://httr2.r-lib.org/reference/resp_body_raw.html) functions to extract the `body` data, depending on the API response format(s).\
The [**API Documentation**](https://developer.themoviedb.org/docs/json-and-jsonp) states the **only supported response format is `JSON`**, so we use the **`resp_body_json()`** function and use the `simplifyVector = T` to make the resulting lists easier to work with.

```{r}
body <- response %>% 
  resp_body_json()
```

Inspecting the body shows it is a list with 4 elements.  

```{r}
lapply(body, class)
```

The `$page`, `$total_pages`, and `$total_results` elements are all `integer` values:

```{r}
body[c("page", "total_pages", "total_results")]
```

The `$results` element is a nested list from the `json` response which then uses `tidyr::unnest_wider()` to clean the data and get a result in a data frame (`tibble::tibble()`)

```{r}
tibble::tibble(results = body$results) %>% 
  tidyr::unnest_wider(results) %>% 
  dplyr::glimpse()
  
```

### Missing Data

The `body$total_results` is `r body$total_results`, yet the `body$results` only contain `r length(body$results)` rows.\
This is because **`r paste("body$total_pages =", body$total_pages)`** but each response only returns **one** page.

To get the other pages, we need to specify an additional argument **`page = n`** to the response, like so:

```{r}
page2_response <- base_request %>% 
  req_url_path_append("search", "movie") %>% 
  req_url_query(query = "Avengers",
                page = 2) %>%                ### NEW ARGUMENT
  req_perform() %>% 
  resp_body_json(simplifyVector = T) 

tibble::tibble(results = page2_response$results ) %>% 
  tidyr::unnest_wider(results) %>% 
  dplyr::glimpse()
```

This 'second page' table contains the *next* `r nrow(page2_response$results)` rows.\
To get all rows we need to repeat this until `r paste("page =", page2_response$total_pages)`


To combine all of the pages from the search we can simply call the wrapper function:

```{r eval = secret_has_key("HTTR2_KEY")}
search_movies(query = "Avengers",
              auth_token = decrypt_auth_token()) %>% 
  dplyr::glimpse()
```

