---
title: "imdb_data"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Load Packages and Data
```{r results=F, collapse=T, warning=F, message=F}
library(tmdbdata)
library(dplyr)
library(ggplot2)
library(ggridges)
library(scales)
```

```{r results=F, warning=F}
imdb_data <- load_imdb_data()
rated_media <- imdb_data$rated_media %>% mutate(runtimeMinutes = as.double(runtimeMinutes))
tv_episodes <- imdb_data$tv_episodes
```

# Determine data structure
```{r}
rated_media %>% glimpse()
```
# Number of observations
```{r}
count_by_type <- rated_media %>% 
  group_by(titleType) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count)) %>% 
  mutate(count = count %>%
           prettyNum(big.mark = ","))

count_by_type
```


```{r}
# Reorder titleTypes for future plots
rated_media$titleType <- factor(rated_media$titleType,
                                levels = count_by_type$titleType)
```

## Rating vs Votes
```{r fig.width=8}
rated_media %>% 
  ggplot(aes(x=numVotes, y=averageRating)) + 
  geom_bin_2d()+
  scale_x_log10(labels = label_comma()) + 
  scale_y_continuous(breaks = seq(0,10,2))+
  scale_fill_viridis_c(option = 'mako',
                       labels = label_comma(),
                       transform = scales::transform_log10()) +
  labs(title = "Rating vs #Votes") +
  facet_wrap(~ titleType,
             ncol = 3)

```
## Rating vs Runtime
```{r fig.width=8}
rated_media %>% 
  filter(runtimeMinutes < 3*60) %>% 
  # filter(titleType != "tvEpisode") %>%
  ggplot(aes(x=runtimeMinutes, y=averageRating)) + 
  geom_bin_2d()+
  scale_x_continuous(breaks = seq(0,300,60),
                     labels = paste0(0:5,"h"),
                     name = "Runtime (Hours)") + 
  scale_y_continuous(breaks = seq(0,10,2))+
  scale_fill_viridis_c(option = 'rocket',
                       labels = label_comma(),
                       transform = scales::transform_log10()) +
  labs(title = "Rating vs Runtime") +
  facet_wrap(~ titleType,
             ncol = 3)

```


# Distrubutions of parameteres
We can see vertical 'stripes' of data in above plot, suggesting that the underlying distributions may be of interest.

## Runtime
```{r message=F, fig.width=8}
rated_media %>% 
  mutate(titleType = fct_rev(as_factor(titleType))) %>% 
  filter(runtimeMinutes < 3*60) %>%
  ggplot(aes(x=runtimeMinutes, y=titleType, fill = titleType)) + 
  geom_density_ridges(aes(scale = 1.5),
                      show.legend = F)+
  scale_x_continuous(breaks = seq(0,300,60),
                     labels = paste0(0:5,"h"),
                     name = "Runtime (Hours)") + 
  labs(title = "Runtimes") + 
  theme_minimal()
```
-   Many **`tvEpisode`**s are either **30**mins, **45**mins, or **1**hr  
    +   Similar trend in **`tvSeries`**
-   Most **`movie`**s are ~**1:30 ± 30**mins
-   **`short`**s and **`tvShort`**s don't normally exceed 30 minutes


## Release Year
```{r warning=F, message=F,fig.width=8}
rated_media %>% 
  mutate(titleType = fct_rev(as_factor(titleType))) %>% 
  filter(startYear > 1950) %>%
  ggplot(aes(x=startYear, 
             y=titleType, 
             fill = titleType)) + 
  geom_density_ridges(aes(scale = 1.3),
                      show.legend = F)+
  scale_x_continuous(breaks = seq(1950,2020,10),
                     name = "Release Year") + 
  labs(title = "Release Year") + 
  theme_minimal()
```

# TV Episodes
## Top series (by #votes)
```{r}
rated_media %>% 
  filter(grepl('Series',titleType)) %>% 
  select(tconst, everything(), -titleType, titleType) %>% 
  head(80)
```

## Most Episodes
```{r warning=F, message=F}
tv_episodes %>%
  group_by(tconst_series, series_name) %>% 
  summarize(seasons = length(unique(seasonNumber)),
            episodes = n(),
            start = min(episode_year, na.rm = T),
            last = max(episode_year, na.rm = T)) %>% 
  arrange(desc(episodes)) %>% 
  ungroup() %>% 
  head(80)
```

## Episode Heatmap
```{r fig.width=12}
series_id <- "tt0096697" # id for "The Simpsons"

series_episodes <- tv_episodes %>% 
  filter(tconst_series == series_id,
         episodeNumber > 0) %>% 
  arrange(seasonNumber,episodeNumber)

# Add in x and y coordinates to draw boxes
plot_eps <- series_episodes %>% 
  select(series_name:episode_rating) %>% 
  mutate(x_start = episodeNumber - 0.5,
         x_end = episodeNumber + 0.5,
         y_start = seasonNumber - 0.5,
         y_end = seasonNumber + 0.5) %>% 
  pivot_longer(c(x_start,x_end),
               names_to = NULL,
               values_to = "x") %>% 
  pivot_longer(c(y_start,y_end),
               names_to = NULL,
               values_to = "y") %>% 
  group_by(seasonNumber, episodeNumber, episode_name) %>% 
  mutate(draw_order = case_when(x == min(x) & y == min(y) ~ 1,
                                x == min(x) & y == max(y) ~ 2,
                                x == max(x) & y == max(y) ~ 3,
                                x == max(x) & y == min(y) ~ 4)) %>% 
  arrange(seasonNumber, episodeNumber, draw_order)
  
  
plot_eps %>% 
  ggplot(aes(x=episodeNumber,
             y=seasonNumber,
             group = paste(seasonNumber, episodeNumber),
             # color = episode_rating,
             fill = episode_rating)) + 
  geom_polygon(aes(x=x, y=y)) +         #COORDINATES USED HERE
  geom_text(aes(label = episode_rating)) + 
  scale_fill_distiller(palette = 'RdYlGn',
                       direction = 1,
                       limits = c(5,10),
                       label = label_number(accuracy = 1),
                       name = 'IMDB Rating') + 
  scale_x_continuous(breaks = seq(1, max(series_episodes$episodeNumber),1),
                     name = "Episode") +  
  scale_y_reverse(breaks = 1:max(series_episodes$seasonNumber),
                  name = "Season") + 
  labs(title = series_episodes$series_name[1]) + 
  theme_minimal() + 
  theme(axis.line = element_blank(),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.major.x = element_line(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        plot.title = element_text(size = 20, face = "bold"),
        axis.title = element_text(size = 20),
        axis.text = element_text(face = "bold",
                                 size = 15))

```

## Top episodes:
```{r fig.width=8}
topten_episodes <- series_episodes %>% 
  arrange(desc(episode_rating)) %>% 
  mutate(season_episode = paste0(seasonNumber,
                                 "–",
                                 episodeNumber)) %>% 
  select(season_episode,
         episode_name,
         episode_rating,
         numVotes,
         episode_year) %>% 
  head(20)

ymin <- 5
topten_episodes %>% 
  mutate(ratingoffset = episode_rating - ymin,
         season_episode = factor(season_episode, 
                                 levels = season_episode)) %>% 
  ggplot(aes(x=season_episode, 
             y = ratingoffset, 
             fill = episode_rating)) +
  geom_col(color = 'black') +
  geom_text(aes(label = episode_name,
                y=0.1,
                angle = 90,
                hjust = 0))+
  geom_text(aes(label = episode_rating,
                vjust = -0.2))+
  scale_y_continuous(labels = function(n) n + ymin,
                     name = "Rating") +
  theme(axis.text.x = element_text(angle = 45,
                                   vjust = 0.8))+
  scale_fill_distiller(palette = 'RdYlGn',
                       direction = 1,
                       limits = c(5,10),
                       label = label_number(accuracy = 1),
                       name = 'IMDB Rating')
```

## Season Ratings:
```{r}
season_ratings <- series_episodes %>% 
  group_by(seasonNumber) %>% 
  summarize(rating = mean(episode_rating) %>% round(1))

ymin <- 5
season_ratings %>% 
  mutate(ratingoffset = rating - ymin) %>% 
  ggplot(aes(x = seasonNumber, y = ratingoffset, fill = rating)) + 
  geom_col(color = 'black') +
  scale_y_continuous(labels = function(n) n + ymin,
                     name = 'Rating') +
  scale_fill_distiller(palette = 'RdYlGn',
                       direction = 1,
                       limits = c(5,10),
                       label = label_number(accuracy = 1),
                       name = 'IMDB Rating') 
```

